---
title: "simple2.Rmd"
author: "Sam"
date: "6/15/2018"
output: html_document
vignette: >
  %\VignetteIndexEntry{Simple Data Access}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Package

`rh5pydclient` is a R wrapper for the python package `h5pyd`. 

```{r}
library(rh5pydclient)
```

### Initialization

Initialize python and check for required packages.

```{r}
initPython()
```

### Connect to the server

This server is an AWS instance with ID `i-046c975236be75444`. It is not usually running. To run
this vignette, email Sam and ask to have it started. 

Connect to a `h5serv` or `hsds` server and identify a H5 file to open.

```{r}
endpoint = 'http://54.224.146.67:5000'
domain = 'tinyfile.public.gliobulk.org'
conn <- initConn(domain=domain, mode='r+', endpoint=endpoint)
```

### Open a dataset

Obtain a handle to a dataset.

```{r}
D <- getDataset(conn, 'tinyds')
```

### Upload data

At present, the only way to signify the submatrix to fetch or store to is to pass slices as constant 
R strings in the format `start:stop:step`. The indices should be in R convention, i.e.,
the first array subscript is 1 (not 0) and if `stop-start` is a multiple of `step`, 
the index `stop` is included in the slice.

```{r}
A <- array(c(4, 14, 7, 17, 5, 15, 9, 19), dim=c(2, 2, 2))
setSubmatrix(D, c('7:8:1', '11:12:1', '11:12:1'), A)
# check
getSubmatrix(D, c('7:8:1', '11:12:1', '11:12:1'))
```



