---
title: "simple.Rmd"
author: "Sam"
date: "6/15/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Package

\code{rh5pydclient} is a R wrapper for the python package \code{h5pyd}. 

```{r}
library(rh5pydclient)
```

### Initialization

The user must have a python executable, the R package \code{reticulate} and the python package \code{h5pyd} installed. The \code{initPython} initializes access to python and checks that \code{h5pyd} is installed. The user can set the path to the preferred python executable. By default, \code{reticulate} will search for a python executable to use.

```{r}
initPython()
```

### Connect to the server

Connect to a \code{h5serv} or \code{hsds} server and identify a H5 file to open.

```{r}
conn <- initConn(domain='/home/stvjc/tenx_full.h5', endpoint='http://52.4.181.237:5101')
```

### Open a dataset

Obtain a handle to a dataset.

```{r}
D <- getDataset(conn, 'newassay001')
```

### Download data

At present, the only way to signify the submatrix to fetch is to pass slices as constant 
R strings in the format \code{start:stop:step}. The indices should be in R convention, i.e.,
the first array subscript is 1 (not 0) and if \code{stop-start} is a multiple of \code{step}, 
the index \code{stop} is included in the slice.

```{r}
A <- getSubmatrix(conn, D, c('200:300:1', '400:500:1'))
sum(A)    # should be 2000
```



