---
title: "simple.Rmd"
author: "Sam"
date: "6/15/2018"
output: html_document
vignette: >
  %\VignetteIndexEntry{Simple Data Access}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Package

`rh5pydclient` is a R wrapper for the python package `h5pyd`. 

```{r}
library(rh5pydclient)
```

### Initialization

The user must have a python executable, the R package `reticulate` and the python package `h5pyd` installed. The `initPython` initializes access to python and checks that `h5pyd` is installed. The user can set the path to the preferred python executable. By default, `reticulate` will search for a python executable to use.

```{r}
initPython()
```

### Connect to the server

Connect to a `h5serv` or `hsds` server and identify a H5 file to open.

```{r}
conn <- initConn(domain='/home/stvjc/tenx_full.h5', endpoint='http://52.4.181.237:5101')
```

### Open a dataset

Obtain a handle to a dataset.

```{r}
D <- getDataset(conn, 'newassay001')
```

### Download data

At present, the only way to signify the submatrix to fetch is to pass slices as constant 
R strings in the format `start:stop:step`. The indices should be in R convention, i.e.,
the first array subscript is 1 (not 0) and if `stop-start` is a multiple of `step`, 
the index `stop` is included in the slice.

```{r}
A <- getSubmatrix(conn, D, c('200:300:1', '400:600:1'))
sum(A)    # should be 2848
```



